---
title: "BIOL6220_Fall2022_RTutorial"
output:
  html_document:
    df_print: paged
---

# R Basic

## Introduction

R as a calculator 
```{r}
1 + 100
```

```{r}
2^2
```

```{r}
4-1
```

```{r}
2*2
```

```{r}
3+5*2
```

```{r}
(3+5)*2
```

```{r}
2e2
```

```{r}
2/10000
```

```{r}
log(1)
```

```{r}
exp(0)
```

```{r}
1 == 1
```

```{r}
1 >= 1
1 < 1
```

```{r}
x <- 10
x + x
```

```{r}
y <- x+x
y
```

### Vectorization

```{r}
1:5
```

```{r}
2^(1:5)
```

```{r}
v <- 1:5
2^v
```
```{r}
log10(v)
```

### Environment 

```{r}
ls()
```

```{r}
rm(v)
```

```{r}
ls()
```

## Package Management 

```{r}
installed.packages()
```

```{r}
#install.packages("vegan", dependencies=TRUE)
```
```{r}
library(vegan)
```

```{r}
#remove.packages("vegan")
```

##Project Management 

1. Set up management structure (i.e., "data", "src", "results", and "doc")
2. Discuss avoiding redundancy of files
3. Make sure to use version control

##Getting Help

```{r}
?plot
```
```{r}
help(plot)
```

```{r}
vignette("FAQ-vegan")
```

```{r}
citation("vegan")
```

##Data and their formats

```{r}
cats <- data.frame(coat =c("calico", "black", "tabby"),
                   weight = c(2.1, 5, 3.2), 
                   likes_string = c(1, 0, 1))
```
```{r}
cats
```

```{r}
#write.csv(cats, file = "./data/cats.csv")
```
```{r}
#cats <- read.csv("./data/cats.")
```

```{r}
cats$coat
```

```{r}
log(cats$weight)
```

```{r}
logweight <- log(cats$weight)
cbind(cats, logweight)
```

```{r}
cats <- cbind(cats, logweight)
```


```{r}
paste("My cat is", cats$coat, ", and it weighs", cats$weight, "kg.", sep="")
```

### Data Types

```{r}
typeof(cats$coat)
```

```{r}
typeof(cats$weight)
```

```{r}
typeof(cats$likes_string)
```

```{r}
typeof(3.14159)
```

```{r}
typeof("FALSE")
```
```{r}
typeof(T)
typeof(F)
```

```{r}
typeof(cats)
```

```{r}
file.show("./data/cats.csv")
```

```{r}
cats$likes_string <- as.logical(cats$like_string)
typeof(cats$likes_string)
```

```{r}
c("a", "b")
```

```{r}
ab <- c("a", "b")
ab
```

```{r}
c(ab, "c")
```

```{r}
1:10
```

```{r}
seq(10)
```

```{r}
z <- seq(10)
head(z, n=3)
```

```{r}
class(z)
```

```{r}
typeof(z)
```

```{r}
seq(1,100, by=5)
```

### Data Frames 

```{r}
cats
```

```{r}
str(cats$coat)
```

```{r}
coats <- c("tabby", "tortoiseshell", "tortoiseshell", "black", "tabby")
coats
```

```{r}
str(coats)
```

```{r}
factor(coats)
```

```{r}
categories <- factor(coats)
class(coats)
class(categories)
```

```{r}
str(categories)
```

### Lists

```{r}
list_example <-list(title="numbers", numbers=1:10, data=TRUE)
```

```{r}
list_example
```

```{r}
another_list <- list(1, "a", TRUE, 1+1i)
another_list
```

```{r}
typeof(list_example)
class(list_example)
```

```{r}
typeof(cats)
class(cats)
```

```{r}
data.frame(list_example)
```

```{r}
cats

```

```{r}
cats[,3]
```

```{r}
cats[2:3, c(1,3)]
```

### Matricies 

```{r}
matrix_example <- matrix(0, ncol=5, nrow=3)
```

```{r}
matrix_example
```

```{r}
class(matrix_example)
```

```{r}
typeof(matrix_example)
```

```{r}
str(matrix_example)
```

```{r}
dim(matrix_example)
```

```{r}
ncol(matrix_example)
```

```{r}
class(data.frame(matrix_example))
```

```{r}
df_example <- data.frame(matrix_example)
df_example
```

### Subsetting

```{r}
p <- c(2.3, 6.9, 4.0, 23, 1)
p
```

```{r}
names(p) <- c('a', 'b', 'c', 'd', 'e')
p
```

```{r}
p[1]
```

```{r}
p[2:4]
```

```{r}
p[c(1,5)]
```


```{r}
p[c(1,1,1,3,5,5)]
```

```{r}
p[6]
```

```{r}
p[-3]
```

```{r}
p[-(2:4)]
```

```{r}
p[c('a', 'c')]
```

```{r}
p[c(T,F,T,F,T)]
```

```{r}
p[names(p) != 'c']
```

### Factors 

```{r}
f <- factor(c('a', 'b', 'c', 'd', 'e'))
f 
```

```{r}
f[f == 'a']
```

```{r}
f[1:3]
```

```{r}
f[f %in% c('b', 'c')]
```

```{r}
f[-3]
```

```{r}
f2 <- factor(c('a', 'a', 'b', 'c', 'c'))
f2
```

```{r}
f2[f2 == 'a']
```

```{r}
f2[ f2 %in% c('a', 'c')]
```

### Matricies resumed 
```{r}
set.seed(65)
m <- matrix(rnorm(6*4), ncol=4, nrow=6)
m
```
```{r}
m[3:4, c(3,1)]
```
```{r}
m[,c(3,4)]
```
## Lists Revisited

```{r}
xlist <- list(a="BIOL48006220", b=seq(1,10, by = 0.5), data="Grade")
xlist
```
```{r}
xlist[1:2]
```

```{r}
xlist['a']
```

```{r}
xlist[['a']]
```
```{r}
xlist['b']
```
```{r}
xlist[['b']]
```

```{r}
xlist$b
```
### Data Frames Revisited 

```{r}
gp <-read.csv('~/Desktop/Practical Computing /biol48806220_Fall2022/data/forest_area_sq_km.csv')
```
```{r}
head(gp, n=10L)
```
```{r}
head(gp[3], n=10L)
```

```{r}
nrow(gp)
```
```{r}
head(gp[["country"]], 10L)
```
```{r}
gp$X2001
```
```{r}
gp[c(1:3), 2:5]
```
```{r}
gp[ which(gp$X1989 <= 100 & gp$X2019 >= 100),]
```
## Conditionals and Flow
```{r}
n <- 10

if (n < 10) {
 print ("n is less than 10")
}  else if (n > 10) {
  print ("n is greater than 10")
}  else {
  print ("n is equal to 10")
  
}  
```

```{r}
for (n in seq(1,20)) {
  if (n < 10) {
    print ("n is less than 10")
}   else if (n > 10) {
    print ("n is greater than 10")
}   else {
    print ("n is equal to 10")
  }
} 
```
```{r}
g <- 0

while (g <= 10) {
  print(paste(g, "is less than or equal to 10"))
  g <- g+1
}
```

## Plotting and Figures
```{r}
#install.packages("ggplot2")
```

```{r}
library(ggplot2)
```

```{r}
forestdata <- read.csv('~/Desktop/Practical Computing /biol48806220_Fall2022/Data/forest_area_sq_km.csv')

head(forestdata)
```

```{r}
ggplot(data=forestdata, mapping=aes(x=X1989, y=X2019)) + geom_point()
```


































