---
output:
  html_document: default
  pdf_document: default
  
  
#Project Overview

## Intro

#Title: Nitrogen and Phosphorus Remediation in Mesocosm Floating Treatment Wetlands receiving Municipal and Aquacultural Wastewater

#Project Goal: Remediate N and P from wastewater that we amended with additional N and P to bring it back to untreated levels you would see/expect when the wastewater first comes to wastewater treatemtn plant 
Project Objective: To see if addition of plant species to FTW tanks is additive, synergistic, or antagonistic 


#GUC data was converted from basic excel file to csv for use in RStudio. CSV was converted to dataframe for ease of storing and management of data for future operations.   
---
```{r}
gucplant_raw<-as.data.frame(read.csv("~/Desktop/Practical Computing /PracCompFinal/MTB_GUC_Plant Measurements_PracComp.csv", header = TRUE))
gucplant <- na.omit(gucplant_raw)
gucplant
```

```{r}
gucplant.Aseries<-as.data.frame(read.csv("~/Desktop/Practical Computing /PracCompFinal/MTB_GUC_Plant Measurements_PracComp-BREWER.csv", header=TRUE))
#install.packages(car)
#library(car)
```
 
```{r}
#install.packages(c("ggplot2", "ggpubr", "tidyverse", "broom", "AICcmodavg"))
gucplant.Aseries
```


```{r}
#install.packages("ggplot2")
```
#ggplot used to create a variety of plots based on the data provided from the dataframe. In this case it was created using the shoot length data (in cm) sorted by which tank it came from. Root length is being used in the graph following this one. The data is arranged from smallest length to largest with a scatterplot of data points sorted by a single line of the tank. ggplot was used due to its ability to easily change different aspects of the graph with different lines of code. I was able to give the graph a title using the command ggtitle as well as changing the text size using element_text(size=). Changing the size of the text allowed for all the points to be easily readable along the x-axis. 

```{r}
library(hrbrthemes)
library(ggplot2)

gucplant.Aseries.SL<-ggplot(data=gucplant.Aseries, aes(x=gucplant.Aseries$Tank, y=ShootLength)) +
  geom_point(color="Red", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  ggtitle("Shoot Length for All Tanks")
gucplant.Aseries.SL + theme(axis.text.x = element_text(size=8))
gucplant.Aseries.SL
```



```{r}
gucplant.Aseries.RL<-ggplot(data=gucplant.Aseries, aes(x=gucplant.Aseries$Tank, y=RootLength)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  ggtitle("Root Length by Shoot Length Session 1")
gucplant.Aseries.RL + theme(axis.text.x = element_text(size=8))
gucplant.Aseries.RL
```

Boxplots were chosen to see how the data were spread out. The advantage in using the boxplot was that I was able to see the distribution fo the data without taking up as much space with something such as a histogram which was useful because I was able to compare multiple datasets within the same graph. With the boxplot we could observe where the majority of the data lie as well as outliers due ot the use of the five number summary. 

We can see that the pontederia data is skewed towards zero, which makes since due to plants dying off early resulting in that being most of the data. Without outliers present, panicum offers the most centralized dataset. Both juncus and panicum have data with a large number of outliers (juncus with most outliers in the upper quartile and panicum having it spread out amongst first and third quartile). 
```{r}
boxplot(gucplant.Aseries$RootLength ~ gucplant.Aseries$Species)
```

#Shoot length tells a different story than root lenth. Median value of the data were larger due to roots generally being shorter than shoots. Pontederia still has skewed data with the median approaching and the minmimum at the zero value. Pancicum's median favors the upper end of the spectrum and juncus has the median placed at the lower end with a more even spread of the data values. Panicum has the only outlier in the graph. 
```{r}
boxplot(gucplant.Aseries$ShootLength ~ gucplant.Aseries$Species)
```

#Plot of roots by shoots to show association between them. One may expect the longer the roots the longer the shoots as that is an indicator of good plant growth and health. Initially where we name the different data was to associate the data based upon what shows up in the csv file. This is the point of the "which" command in where we are saying that everything that has this word or value associated, bring it over. The lm() command was used to create a linear regression of the grouped data. This way we can predict future data based on what we have currently. abline was used to give a line of best fit for the data. This line of best fit estimates the straight line through the data that minimized the distance between it and all the other points within the graph. col= was used ti associate the line with the color previously given to the data with lty= being used to maximize difference between the lines as to not confuse them. 
```{r}
plot(gucplant.Aseries$RootLength ~ gucplant.Aseries$ShootLength, col=factor(gucplant.Aseries$Species))

Juncus <- gucplant.Aseries[ which(gucplant.Aseries$Species == "Juncus"), ]
Panicum <- gucplant.Aseries[ which(gucplant.Aseries$Species == "Panicum"), ]
Pontederia <- gucplant.Aseries[ which(gucplant.Aseries$Species == "Pontederia"), ]

Juncus.reg <- lm(Juncus$RootLength ~ Juncus$ShootLength)
Panicum.reg <- lm(Panicum$RootLength ~ Panicum$ShootLength)
Pontederia.reg <- lm(Pontederia$RootLength ~ Pontederia$ShootLength)

abline(Juncus.reg, col="black")
abline(Panicum.reg, col="red", lty=2)
abline(Pontederia.reg, col="green", lty=3)
```

#Anova was the next form of data to calculate. This is useful for testing three or more variables at a time, which in this case we have three plant species so this is perfect. This is similar to a two sample t-test, but with ANOVA we are likely to have fewer type 1 errors than the t-test. Within the anova shoot length was tested by species to see if the data is statistically significant from one another. Based on the p-value the data does come back as statistically significant but with ANOVA, it cannot give specifics as to which set of data it is, which is why a Tukey test was run next to compare datasets. 
```{r}
gucplant.Aseries.ANOVA.S <- aov(gucplant.Aseries$ShootLength ~ gucplant.Aseries$Species)
summary(gucplant.Aseries.ANOVA.S)
```

```{r}
TukeyHSD(gucplant.Aseries.ANOVA.S)
```

```{r}
gucplant.Aseries.ANOVA.R <- aov(gucplant.Aseries$RootLength ~ gucplant.Aseries$Species)
summary(gucplant.Aseries.ANOVA.R)
```

```{r}
TukeyHSD(gucplant.Aseries.ANOVA.R)
```

#The guc.Aseries was brought in again using a pairwise test to compare homogeneity amongst the species. The xlabel was the plant species with the y label being the shoot length for this graph and the root length for the graph below. The function ggbetweenstats() was used for its ability to create publication ready plots with relavent statistical analysis. In this case it was used to create a violin plot, which has the advantage over a traditional box plot by giving an more accurate accurate view on the distribution of the data points. From the graph we can see that each of the species is statistically significant from one another. From the confidence interval given we can say with 95% confidence that the mean of the data set is between 0.62 and 1.00 for this specific measure of plant species against shoot length. The r value can tell us that 71% of the points along the graph can be explained and that their is a positive correlation amongst the datapoints for the graph. 
```{r}
library(ggstatsplot)
library(tidyverse)

plt <- ggbetweenstats(
  data = gucplant.Aseries,
  x = Species,
  y = RootLength,
  ylab = "Root Length"
)

plt
```

```{r}
plt2 <- ggbetweenstats(
  data = gucplant.Aseries,
  x = Species,
  y = ShootLength, 
  ylab="Shoot Length"
)

plt2
```

#ggplot was ran again for a comparison of the overall growth of the roots and the shoots of all species within each tank. For the tanks with multiple plant species the plant species were singled out for individual analysis of their performance in the tanks. geom_point() draws the points defined by the x and y variables previously defined and can give them specifics on how they are presented on the graph. Within geom point we can give the points color (color=), tell it how big to make the points (linewidth=), annd the opacity of the points on a scale from 0-1 (alpha=). Within the ggpubr library we get the ggarrange function which allows for the graphs to be placed within a single page to be displayed at the same time. rremove allowed for the removal of the x labels that would have otheriwse been to jumbled to read. The label function gives a name to each graph (tank 1 is "a", tank 2 is "b" and tank 3 is "c") on the page while the ncola and nrow lays out the grid of how the graphs show up. In this case it is a 2x2 pattern. 
```{r}
gucplantbytankA1s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$A1.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankA1s

gucplantbytankA2s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$A2.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankA2s

gucplantbytankA3s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$A3.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankA3s

library(ggpubr)
ggarrange(gucplantbytankA1s + rremove("x.text"), gucplantbytankA2s + rremove("x.text"), gucplantbytankA3s + rremove("x.text"),
          labels = c("A", "B", "C"), 
          ncol =2, nrow =2)
```




```{r}
gucplantbytankA1r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$A1.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankA1r

gucplantbytankA2r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$A2.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankA2r

gucplantbytankA3r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$A3.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankA3r

ggarrange(gucplantbytankA1r + rremove("x.text"), gucplantbytankA2r + rremove("x.text"), gucplantbytankA3r + rremove("x.text"),
          labels = c("A", "B", "C"), 
          ncol =2, nrow =2)
```

```{r}
gucplantbytankB1r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$B1.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankB1r

gucplantbytankB2r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$B2.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankB2r

gucplantbytankB3r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$B3.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankB3r

ggarrange(gucplantbytankB1r + rremove("x.text"), gucplantbytankB2r + rremove("x.text"), gucplantbytankB3r + rremove("x.text"),
          labels = c("A", "B", "C"), 
          ncol =2, nrow =2)
```

```{r}
gucplantbytankB1s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$B1.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankB1r

gucplantbytankB2s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$B2.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankB2s

gucplantbytankB3s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$B3.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankB3s

ggarrange(gucplantbytankB1s + rremove("x.text"), gucplantbytankB2s + rremove("x.text"), gucplantbytankB3s + rremove("x.text"),
          labels = c("A", "B", "C"), 
          ncol =2, nrow =2)
```

```{r}
gucplantbytankC1r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$C1.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankC1r

gucplantbytankC2r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$C2.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankC2r

gucplantbytankC3r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$C3.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankC3r

ggarrange(gucplantbytankC1r + rremove("x.text"), gucplantbytankC2r + rremove("x.text"), gucplantbytankC3r + rremove("x.text"),
          labels = c("A", "B", "C"), 
          ncol =2, nrow =2)
```

```{r}
gucplantbytankC1s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$C1.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankC1s

gucplantbytankC2s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$C2.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankC2s

gucplantbytankC3s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$C3.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankC3s

ggarrange(gucplantbytankC1s + rremove("x.text"), gucplantbytankC2s + rremove("x.text"), gucplantbytankC3s + rremove("x.text"),
          labels = c("A", "B", "C"), 
          ncol =2, nrow =2)
```
```{r}
gucplantbytankABJ1r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABJ1.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABJ1r

gucplantbytankABJ2r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABJ2.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABJ2r

gucplantbytankABJ3r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABJ3.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABJ3r

ggarrange(gucplantbytankABJ1r + rremove("x.text"), gucplantbytankABJ2r + rremove("x.text"), gucplantbytankABJ3r + rremove("x.text"),
          labels = c("A", "B", "C"), 
          ncol =2, nrow =2)
```

```{r}
gucplantbytankABJ1s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABJ1.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABJ1s

gucplantbytankABJ2s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABJ2.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABJ2s

gucplantbytankABJ3s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABJ3.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABJ3s

ggarrange(gucplantbytankABJ1s + rremove("x.text"), gucplantbytankABJ2s + rremove("x.text"), gucplantbytankABJ3s + rremove("x.text"),
          labels = c("A", "B", "C"), 
          ncol =2, nrow =2)
```

```{r}
gucplantbytankABPo1r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABPo1.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABPo1r

gucplantbytankABPo2r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABPo2.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABPo2r

gucplantbytankABPo3r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABPo3.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABPo3r

ggarrange(gucplantbytankABPo1r + rremove("x.text"), gucplantbytankABPo2r + rremove("x.text"), gucplantbytankABPo3r + rremove("x.text"),
          labels = c("A", "B", "C"), 
          ncol =2, nrow =2)
```

```{r}
gucplantbytankACJ1r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ACJ1.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankACJ1r

gucplantbytankACJ2r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ACJ2.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankACJ2r

gucplantbytankACJ3r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ACJ3.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankACJ3r

ggarrange(gucplantbytankACJ1r + rremove("x.text"), gucplantbytankACJ2r + rremove("x.text"), gucplantbytankACJ3r + rremove("x.text"),
          labels = c("A", "B", "C"), 
          ncol =2, nrow =2)
```

```{r}
gucplantbytankACJ1s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ACJ1.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankACJ1s

gucplantbytankACJ2s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ACJ2.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankACJ2s

gucplantbytankACJ3s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ACJ3.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankACJ3s

ggarrange(gucplantbytankACJ1s + rremove("x.text"), gucplantbytankACJ2s + rremove("x.text"), gucplantbytankACJ3s + rremove("x.text"),
          labels = c("A", "B", "C"), 
          ncol =2, nrow =2)
```

```{r}
gucplantbytankACPa1r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ACPa1.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankACPa1r

gucplantbytankACPa2r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ACPa2.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankACPa2r

gucplantbytankACPa3r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ACPa3.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankACPa3r

ggarrange(gucplantbytankACPa1r + rremove("x.text"), gucplantbytankACPa2r + rremove("x.text"), gucplantbytankACPa3r + rremove("x.text"),
          labels = c("A", "B", "C"), 
          ncol =2, nrow =2)
```

```{r}
gucplantbytankACPa1s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ACPa1.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankACPa1s

gucplantbytankACPa2s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ACPa2.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankACPa2s

gucplantbytankACPa3s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ACPa3.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankACPa3s

ggarrange(gucplantbytankACPa1s + rremove("x.text"), gucplantbytankACPa2s + rremove("x.text"), gucplantbytankACPa3s + rremove("x.text"),
          labels = c("A", "B", "C"), 
          ncol =2, nrow =2)
```

```{r}
gucplantbytankBCPa1r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$BCPa1.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankBCPa1r

gucplantbytankBCPa2r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$BCPa2.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankBCPa2r

gucplantbytankBCPa3r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$BCPa3.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankBCPa3r

ggarrange(gucplantbytankBCPa1r + rremove("x.text"), gucplantbytankBCPa2r + rremove("x.text"), gucplantbytankBCPa3r + rremove("x.text"),
          labels = c("A", "B", "C"), 
          ncol =2, nrow =2)
```

```{r}
gucplantbytankBCPo1r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$BCPo1.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankBCPo1r

gucplantbytankBCPo2r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$BCPo2.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankBCPo2r

gucplantbytankBCPo3r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$BCPo3.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankBCPo3r

ggarrange(gucplantbytankBCPo1r + rremove("x.text"), gucplantbytankBCPo2r + rremove("x.text"), gucplantbytankBCPo3r + rremove("x.text"),
          labels = c("A", "B", "C"), 
          ncol =2, nrow =2)
```

```{r}
gucplantbytankBCPo1s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$BCPo1.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankBCPo1r

gucplantbytankBCPo2s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$BCPo2.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankBCPo2s

gucplantbytankBCPo3s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$BCPo3.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankBCPo3s

ggarrange(gucplantbytankBCPo1s + rremove("x.text"), gucplantbytankBCPo2s + rremove("x.text"), gucplantbytankBCPo3s + rremove("x.text"),
          labels = c("A", "B", "C"), 
          ncol =2, nrow =2)
```

```{r}
gucplantbytankABCPo1r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABCPo1.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABCPo1r

gucplantbytankABCPo2r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABCPo2.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABCPo2r

gucplantbytankABCPo3r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABCPo3.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABCPo3r

ggarrange(gucplantbytankABCPo1r + rremove("x.text"), gucplantbytankABCPo2r + rremove("x.text"), gucplantbytankABCPo3r + rremove("x.text"),
          labels = c("A", "B", "C"), 
          ncol =2, nrow =2)
```

```{r}
gucplantbytankABCPo1s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABCPo1.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABCPo1s

gucplantbytankABCPo2s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABCPo2.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABCPo2s

gucplantbytankABCPo3s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABCPo3.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABCPo3s

ggarrange(gucplantbytankABCPo1s + rremove("x.text"), gucplantbytankABCPo2s + rremove("x.text"), gucplantbytankABCPo3s + rremove("x.text"),
          labels = c("A", "B", "C"), 
          ncol =2, nrow =2)
```

```{r}
gucplantbytankABCPa1r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABCPa1.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABCPa1r

gucplantbytankABCPa2r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABCPa2.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABCPa2r

gucplantbytankABCPa3r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABCPa3.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABCPa3r

ggarrange(gucplantbytankABCPa1r + rremove("x.text"), gucplantbytankABCPa2r + rremove("x.text"), gucplantbytankABCPa3r + rremove("x.text"),
          labels = c("A", "B", "C"), 
          ncol =2, nrow =2)
```

```{r}
gucplantbytankABCPa1s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABCPa1.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABCPa1s

gucplantbytankABCPa2s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABCPa2.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABCPa2s

gucplantbytankABCPa3s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABCPa3.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABCPa3s

ggarrange(gucplantbytankABCPa1s + rremove("x.text"), gucplantbytankABCPa2s + rremove("x.text"), gucplantbytankABCPa3s + rremove("x.text"),
          labels = c("A", "B", "C"), 
          ncol =2, nrow =2)
```

```{r}
gucplantbytankABCJ1r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABCJ1.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABCJ1r

gucplantbytankABCJ2r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABCJ2.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABCJ2r

gucplantbytankABCJ3r <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABCJ3.r)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABCJ3r

ggarrange(gucplantbytankABCJ1r + rremove("x.text"), gucplantbytankABCJ2r + rremove("x.text"), gucplantbytankABCJ3r + rremove("x.text"),
          labels = c("A", "B", "C"), 
          ncol =2, nrow =2)
```

```{r}
gucplantbytankABCJ1s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABCJ1.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABCJ1s

gucplantbytankABCJ2s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABCJ2.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABCJ2s

gucplantbytankABCJ3s <- ggplot(data = gucplant, aes(x=gucplant$Date, y=gucplant$ABCJ3.s)) +
  geom_point(color="Blue", linewidth=2, alpha=0.9) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = 8))
gucplantbytankABCJ3s

ggarrange(gucplantbytankABCJ1s + rremove("x.text"), gucplantbytankABCJ2s + rremove("x.text"), gucplantbytankABCJ3s + rremove("x.text"),
          labels = c("A", "B", "C"), 
          ncol =2, nrow =2)
```

```{r}
x=gucplant$A1.s
y=gucplant$A2.s
gucplant.ttest.A.S12 <- t.test(gucplant$A1.s, gucplant$A2.s)
gucplant.ttest.A.S12
```

```{r}

gucplant.ttest.A.S13 <- t.test(gucplant$A1.s, gucplant$A3.s)
gucplant.ttest.A.S13
```

```{r}
gucplant.ttest.A.S23 <- t.test(gucplant$A3.s, gucplant$A2.s)
gucplant.ttest.A.S23
```

```{r}
gucplant.ttest.A.R12 <- t.test(gucplant$A1.r, gucplant$A2.r)
gucplant.ttest.A.R12
```

```{r}
gucplant.ttest.A.R23 <- t.test(gucplant$A3.r, gucplant$A2.r)
gucplant.ttest.A.R23
```

```{r}
gucplant.ttest.A.R13 <- t.test(gucplant$A1.r, gucplant$A3.r)
gucplant.ttest.A.R13
```

```{r}
gucplant.ttest.B.R12 <- t.test(gucplant$B1.r, gucplant$B2.r)
gucplant.ttest.B.R12
```

```{r}
gucplant.ttest.B.R13 <- t.test(gucplant$B1.r, gucplant$B3.r)
gucplant.ttest.B.R13
```

```{r}
gucplant.ttest.B.R23 <- t.test(gucplant$B3.r, gucplant$B2.r)
gucplant.ttest.B.R23
```

```{r}
gucplant.ttest.B.S12 <- t.test(gucplant$B1.s, gucplant$B2.s)
gucplant.ttest.B.S12
```

```{r}
gucplant.ttest.B.S13 <- t.test(gucplant$B1.s, gucplant$B3.s)
gucplant.ttest.B.S13
```

```{r}
gucplant.ttest.B.S23 <- t.test(gucplant$B3.s, gucplant$B2.s)
gucplant.ttest.B.S23
```

```{r}
gucplant.ttest.C.R12 <- t.test(gucplant$C1.r, gucplant$C2.r)
gucplant.ttest.C.R12
```

```{r}
gucplant.ttest.C.R13 <- t.test(gucplant$C1.r, gucplant$C3.r)
gucplant.ttest.C.R13
```

```{r}
gucplant.ttest.C.R23 <- t.test(gucplant$C3.r, gucplant$C2.r)
gucplant.ttest.C.R23
```

```{r}
gucplant.ttest.C.S12 <- t.test(gucplant$C1.s, gucplant$C2.s)
gucplant.ttest.C.S12
```

```{r}
gucplant.ttest.C.S13 <- t.test(gucplant$C1.s, gucplant$C3.s)
gucplant.ttest.C.S13
```

```{r}
gucplant.ttest.C.S23 <- t.test(gucplant$C3.s, gucplant$C2.s)
gucplant.ttest.C.S23
```

```{r}
gucplant.ttest.AB.R12 <- t.test(gucplant$ABJ1.r, gucplant$ABJ2.r)
gucplant.ttest.AB.R12
```

```{r}
gucplant.ttest.AB.R13 <- t.test(gucplant$ABJ1.r, gucplant$ABJ3.r)
gucplant.ttest.AB.R12
```

```{r}
gucplant.ttest.AB.R23 <- t.test(gucplant$ABJ3.r, gucplant$ABJ2.r)
gucplant.ttest.AB.R23
```

```{r}
gucplant.ttest.AB.S12 <- t.test(gucplant$ABJ1.s, gucplant$ABJ2.s)
gucplant.ttest.AB.S12
```

```{r}
gucplant.ttest.AB.S13 <- t.test(gucplant$ABJ1.s, gucplant$ABJ3.s)
gucplant.ttest.AB.S13
```

```{r}
gucplant.ttest.AB.S23 <- t.test(gucplant$ABJ3.s, gucplant$ABJ2.s)
gucplant.ttest.AB.S23
```

```{r}
gucplant.ttest.ABPo.S12 <- t.test(gucplant$ABPo1.s, gucplant$ABPo2.s)
gucplant.ttest.ABPo.S12
```

```{r}
gucplant.ttest.ABPo.S13 <- t.test(gucplant$ABPo1.s, gucplant$ABPo3.s)
gucplant.ttest.ABPo.S13
```

```{r}
gucplant.ttest.ABPo.S23 <- t.test(gucplant$ABPo3.s, gucplant$ABPo2.s)
gucplant.ttest.ABPo.S23
```

```{r}
gucplant.ttest.ABPo.R12 <- t.test(gucplant$ABPo1.r, gucplant$ABPo2.r)
gucplant.ttest.ABPo.R12
```

```{r}
gucplant.ttest.ABPo.R13 <- t.test(gucplant$ABPo1.r, gucplant$ABPo3.r)
gucplant.ttest.ABPo.R13
```

```{r}
gucplant.ttest.ABPo.R23 <- t.test(gucplant$ABPo3.r, gucplant$ABPo2.r)
gucplant.ttest.ABPo.R23
```

```{r}
gucplant.ttest.ACJ.R12 <- t.test(gucplant$ACJ1.r, gucplant$ACJ2.r)
gucplant.ttest.ACJ.R12
```

```{r}
gucplant.ttest.ACJ.R13 <- t.test(gucplant$ACJ1.r, gucplant$ACJ3.r)
gucplant.ttest.ACJ.R13
```

```{r}
gucplant.ttest.ACJ.R23 <- t.test(gucplant$ACJ2.r, gucplant$ACJ3.r)
gucplant.ttest.ACJ.R23
```

```{r}
gucplant.ttest.ACJ.S12 <- t.test(gucplant$ACJ1.s, gucplant$ACJ2.s)
gucplant.ttest.ACJ.S12
```

```{r}
gucplant.ttest.ACJ.S13 <- t.test(gucplant$ACJ1.s, gucplant$ACJ3.s)
gucplant.ttest.ACJ.S13
```

```{r}
gucplant.ttest.ACJ.S23 <- t.test(gucplant$ACJ3.s, gucplant$ACJ2.s)
gucplant.ttest.ACJ.S23
```

```{r}
gucplant.ttest.ACPa.S12 <- t.test(gucplant$ACPa1.s, gucplant$ACPa2.s)
gucplant.ttest.ACPa.S12
```

```{r}
gucplant.ttest.ACPa.S13 <- t.test(gucplant$ACPa1.s, gucplant$ACPa3.s)
gucplant.ttest.ACPa.S13
```

```{r}
gucplant.ttest.ACPa.S23 <- t.test(gucplant$ACPa3.s, gucplant$ACPa2.s)
gucplant.ttest.ACPa.S23
```

```{r}
gucplant.ttest.ACPa.R12 <- t.test(gucplant$ACPa1.r, gucplant$ACPa2.r)
gucplant.ttest.ACPa.R12
```

```{r}
gucplant.ttest.ACPa.R13 <- t.test(gucplant$ACPa3.r, gucplant$ACPa1.r)
gucplant.ttest.ACPa.R13
```

```{r}
gucplant.ttest.ACPa.R23 <- t.test(gucplant$ACPa3.r, gucplant$ACPa2.r)
gucplant.ttest.ACPa.R23
```

```{r}
gucplant.ttest.ABCJ.R12<- t.test(gucplant$ABCJ1.r, gucplant$ABCJ2.r)
gucplant.ttest.ABCJ.R12
```

```{r}
gucplant.ttest.ABCJ.R13<- t.test(gucplant$ABCJ1.r, gucplant$ABCJ3.r)
gucplant.ttest.ABCJ.R13
```

```{r}
gucplant.ttest.ABCJ.R23<- t.test(gucplant$ABCJ3.r, gucplant$ABCJ2.r)
gucplant.ttest.ABCJ.R23
```

```{r}
gucplant.ttest.ABCJ.S12<- t.test(gucplant$ABCJ1.s, gucplant$ABCJ2.s)
gucplant.ttest.ABCJ.S12
```

```{r}
gucplant.ttest.ABCJ.S13<- t.test(gucplant$ABCJ1.s, gucplant$ABCJ3.s)
gucplant.ttest.ABCJ.R12
```

```{r}
gucplant.ANOVA.ABCJ.S23<- aov(gucplant$ABCJ3.s ~ gucplant$ABCJ2.s)
summary(gucplant.ANOVA.ABCJ.S23)
```

```{r}
gucplant.ANOVA.ABCPo.R12 <- aov(gucplant$ABCPo1.r ~ gucplant$ABCPo2.r)
summary(gucplant.ANOVA.ABCPo.R12)
```

```{r}
gucplant.ANOVA.ABCPo.R13 <- aov(gucplant$ABCPo1.r ~ gucplant$ABCPo3.r)
summary(gucplant.ANOVA.ABCPo.R13)
```

```{r}
gucplant.ANOVA.ABCPo.R23 <- aov(gucplant$ABCPo2.r ~ gucplant$ABCPo3.r)
summary(gucplant.ANOVA.ABCPo.R23)
```

```{r}
gucplant.ANOVA.ABCPo.S12 <- aov(gucplant$ABCPo1.s ~ gucplant$ABCPo3.s)
summary(gucplant.ANOVA.ABCPo.S12)
```

```{r}
gucplant.ANOVA.ABCPo.S13 <- aov(gucplant$ABCPo1.s ~ gucplant$ABCPo3.s)
summary(gucplant.ANOVA.ABCPo.S13)
```

```{r}
gucplant.ANOVA.ABCPo.S23 <- aov(gucplant$ABCPo2.s ~ gucplant$ABCPo3.s)
summary(gucplant.ANOVA.ABCPo.S23)
```

```{r}
gucplant.ANOVA.ABCPa.R12 <- aov(gucplant$ABCPa1.r ~ gucplant$ABCPa2.r)
summary(gucplant.ANOVA.ABCPa.R12)
```

```{r}
gucplant.ANOVA.ABCPa.R13 <- aov(gucplant$ABCPa1.r ~ gucplant$ABCPa3.r)
summary(gucplant.ANOVA.ABCPa.R13)
```

```{r}
gucplant.ANOVA.ABCPa.R23 <- aov(gucplant$ABCPa3.r ~ gucplant$ABCPa2.r)
summary(gucplant.ANOVA.ABCPa.R23)
```

```{r}
gucplant.ANOVA.ABCPa.S13 <- aov(gucplant$ABCPa1.s ~ gucplant$ABCPa2.s)
summary(gucplant.ANOVA.ABCPa.S13)
```

```{r}
gucplant.ANOVA.ABCPa.S13 <- aov(gucplant$ABCPa1.s ~ gucplant$ABCPa3.s)
summary(gucplant.ANOVA.ABCPa.S13)
```

```{r}
gucplant.ANOVA.ABCPa.S23 <- aov(gucplant$ABCPa2.s ~ gucplant$ABCPa3.s)
summary(gucplant.ANOVA.ABCPa.S23)
```

```{r}
gucplant.ANOVA.AB1.R <- aov(gucplant$A1.r ~ gucplant$B1.r)
summary(gucplant.ANOVA.AB1.R)
```

```{r}
gucplant.ANOVA.AC1.R <- aov(gucplant$A1.r ~ gucplant$C1.r)
summary(gucplant.ANOVA.AC1.R)
```

```{r}
gucplant.ANOVA.AB2.R <- aov(gucplant$A2.r ~ gucplant$B2.r)
summary(gucplant.ANOVA.AB2.R)
```

```{r}
gucplant.ANOVA.AC2.R <- aov(gucplant$A2.r ~ gucplant$C2.r)
summary(gucplant.ANOVA.AC2.R)
```

```{r}
gucplant.ANOVA.AB3.R <- aov(gucplant$A3.r ~ gucplant$B3.r)
summary(gucplant.ANOVA.AB3.R)
```

```{r}
gucplant.ANOVA.AC3.R <- aov(gucplant$A3.r ~ gucplant$C3.r)
summary(gucplant.ANOVA.AC3.R)
```

```{r}
gucplant.ANOVA.AB1.S <- aov(gucplant$A1.s ~ gucplant$B1.s)
summary(gucplant.ANOVA.AB1.S)
```

```{r}
gucplant.ANOVA.AB2.S <- aov(gucplant$A2.s ~ gucplant$B2.s)
summary(gucplant.ANOVA.AB2.S)
```

```{r}
gucplant.ANOVA.AB3.S <- aov(gucplant$A3.s ~ gucplant$B3.s)
summary(gucplant.ANOVA.AB3.S)
```

```{r}
gucplant.ANOVA.AC1.S <- aov(gucplant$A1.s ~ gucplant$C1.s)
summary(gucplant.ANOVA.AC1.S)
```

```{r}
gucplant.ANOVA.AC2.S <- aov(gucplant$A2.s ~ gucplant$C2.s)
summary(gucplant.ANOVA.AC2.S)
```

```{r}
gucplant.ANOVA.AC3.S <- aov(gucplant$A3.s ~ gucplant$C3.s)
summary(gucplant.ANOVA.AC3.S)
```

```{r}
gucplant.ANOVA.BC1.S <- aov(gucplant$B1.s ~ gucplant$C1.s)
summary(gucplant.ANOVA.BC1.S)
```

```{r}
gucplant.ANOVA.BC2.S <- aov(gucplant$B2.s ~ gucplant$C2.s)
summary(gucplant.ANOVA.BC2.S)
```

```{r}
gucplant.ANOVA.BC3.S <- aov(gucplant$B3.s ~ gucplant$C3.s)
summary(gucplant.ANOVA.BC3.S)
```

```{r}
gucplant.ANOVA.BC1.R <- aov(gucplant$B1.r ~ gucplant$C1.r)
summary(gucplant.ANOVA.BC1.R)
```

```{r}
gucplant.ANOVA.BC2.R <- aov(gucplant$B2.r ~ gucplant$C2.r)
summary(gucplant.ANOVA.BC2.R)
```

```{r}
gucplant.ANOVA.BC3.R <- aov(gucplant$B3.r ~ gucplant$C3.r)
summary(gucplant.ANOVA.BC3.R)
```

```{r}
gucplant.ANOVA.ABAC1.R <- aov(gucplant$ABJ1.r ~ gucplant$ACJ1.r)
summary(gucplant.ANOVA.ABAC1.R)
```

```{r}
gucplant.ANOVA.ABAC13.R <- aov(gucplant$ABJ1.r ~ gucplant$ACJ3.r)
summary(gucplant.ANOVA.ABAC13.R)
```

```{r}
gucplant.ANOVA.AB2AC1.R <- aov(gucplant$ABJ2.r ~ gucplant$ACJ1.r)
summary(gucplant.ANOVA.AB2AC1.R)
```

```{r}
gucplant.ANOVA.AB3AC1.R <- aov(gucplant$ABJ3.r ~ gucplant$ACJ1.r)
summary(gucplant.ANOVA.AB3AC1.R)
```

```{r}
gucplant.ANOVA.AB2AC2.R <- aov(gucplant$ABJ2.r ~ gucplant$ACJ2.r)
summary(gucplant.ANOVA.AB2AC2.R)
```

```{r}
gucplant.ANOVA.AB3AC3.R <- aov(gucplant$ABJ2.r ~ gucplant$ACJ3.r)
summary(gucplant.ANOVA.AB3AC3.R)
```

```{r}
gucplant.ANOVA.AB3AC3.R <- aov(gucplant$ABJ3.r ~ gucplant$ACJ3.r)
summary(gucplant.ANOVA.AB3AC3.R)
```

```{r}
gucplant.ANOVA.ABAC1.S <- aov(gucplant$ABJ1.s ~ gucplant$ACJ1.s)
summary(gucplant.ANOVA.ABAC1.S)
```

```{r}
gucplant.ANOVA.ABAC13.S <- aov(gucplant$ABJ1.s ~ gucplant$ACJ3.s)
summary(gucplant.ANOVA.ABAC13.S)
```

```{r}
gucplant.ANOVA.AB2AC1.S <- aov(gucplant$ABJ2.s ~ gucplant$ACJ1.s)
summary(gucplant.ANOVA.AB2AC1.S)
```

```{r}
gucplant.ANOVA.AB3AC1.S <- aov(gucplant$ABJ3.s ~ gucplant$ACJ1.s)
summary(gucplant.ANOVA.AB3AC1.S)
```

```{r}
gucplant.ANOVA.AB2AC2.S <- aov(gucplant$ABJ2.s ~ gucplant$ACJ2.s)
summary(gucplant.ANOVA.AB2AC2.S)
```

```{r}
gucplant.ANOVA.AB2AC3.S <- aov(gucplant$ABJ2.s ~ gucplant$ACJ3.s)
summary(gucplant.ANOVA.AB2AC3.S)
```

```{r}
gucplant.ANOVA.AB3AC3.S <- aov(gucplant$ABJ3.s ~ gucplant$ACJ3.s)
summary(gucplant.ANOVA.AB3AC3.S)
```

```{r}
gucplant.ANOVA.AB1BC1.R <- aov(gucplant$ ABJ1.r ~ gucplant$BCPo1.r)
summary(gucplant.ANOVA.AB1BC1.R)
```

```{r}
gucplant.ANOVA.AB1BC2.R <- aov(gucplant$ ABJ1.r ~ gucplant$BCPo2.r)
summary(gucplant.ANOVA.AB1BC2.R)
```

```{r}
gucplant.ANOVA.AB1BC3.R <- aov(gucplant$ ABJ1.r ~ gucplant$BCPo3.r)
summary(gucplant.ANOVA.AB1BC2.R)
```

```{r}
gucplant.ANOVA.AB2BC1.R <- aov(gucplant$ ABJ2.r ~ gucplant$BCPo1.r)
summary(gucplant.ANOVA.AB2BC1.R)
```

```{r}
gucplant.ANOVA.AB2BC2.R <- aov(gucplant$ ABJ2.r ~ gucplant$BCPo2.r)
summary(gucplant.ANOVA.AB2BC2.R)
```

```{r}
gucplant.ANOVA.AB2BC3.R <- aov(gucplant$ ABJ2.r ~ gucplant$BCPo3.r)
summary(gucplant.ANOVA.AB2BC3.R)
```

```{r}
gucplant.ANOVA.AB3BC1.R <- aov(gucplant$ ABJ3.r ~ gucplant$BCPo1.r)
summary(gucplant.ANOVA.AB3BC1.R)
```

```{r}
gucplant.ANOVA.AB3BC2.R <- aov(gucplant$ ABJ3.r ~ gucplant$BCPo2.r)
summary(gucplant.ANOVA.AB3BC2.R)
```

```{r}
gucplant.ANOVA.AB3BC3.R <- aov(gucplant$ ABJ3.r ~ gucplant$BCPo3.r)
summary(gucplant.ANOVA.AB3BC3.R)
```

```{r}
gucplant.ANOVA.AB1BC1.R <- aov(gucplant$ ABJ1.r ~ gucplant$BCPo1.r)
summary(gucplant.ANOVA.AB1BC1.R)
```

```{r}
gucplant.ANOVA.AB1BC2.S <- aov(gucplant$ ABJ1.s ~ gucplant$BCPo2.s)
summary(gucplant.ANOVA.AB1BC2.S)
```

```{r}
gucplant.ANOVA.AB1BC3.S <- aov(gucplant$ ABJ1.s ~ gucplant$BCPo3.s)
summary(gucplant.ANOVA.AB1BC2.S)
```

```{r}
gucplant.ANOVA.AB2BC1.S <- aov(gucplant$ ABJ2.s ~ gucplant$BCPo1.s)
summary(gucplant.ANOVA.AB2BC1.S)
```

```{r}
gucplant.ANOVA.AB2BC2.S <- aov(gucplant$ ABJ2.s ~ gucplant$BCPo2.s)
summary(gucplant.ANOVA.AB2BC2.S)
```

```{r}
gucplant.ANOVA.AB2BC3.S <- aov(gucplant$ ABJ2.s ~ gucplant$BCPo3.s)
summary(gucplant.ANOVA.AB2BC3.S)
```

```{r}
gucplant.ANOVA.AB3BC1.S <- aov(gucplant$ ABJ3.s ~ gucplant$BCPo1.s)
summary(gucplant.ANOVA.AB3BC1.S)
```

```{r}
gucplant.ANOVA.AB3BC2.S <- aov(gucplant$ ABJ3.s ~ gucplant$BCPo2.s)
summary(gucplant.ANOVA.AB3BC2.S)
```

```{r}
gucplant.ANOVA.AB3BC3.S <- aov(gucplant$ ABJ3.s ~ gucplant$BCPo3.s)
summary(gucplant.ANOVA.AB3BC3.S)
```
